### 2010-02-04 doc/manuals/configuration/configuration_manual.tex
Few more sec handlers described

\subsubsection{ARC Authorization}\label{sec:arcautz-shc}
This Security Handler applies set of Policy Decision Point (PDP) element to the
message and then produces decision result using combining algorithm specified in 
\texttt{action} attribute of \texttt{SecHandler} element. For desciption of PDP
elements see section \ref{sec:Policy Decision Points}.

Available combining algorithms are:
\begin{description}
\item[breakOnDeny] - processing stops when PDP returns Deny decision. The SecHandler
produces negative result. This is a default algorith.
\item[breakOnAllow] - processing stopr when PDP return Allow decision. The SecHandler
produces positive result.
\item[breakAlways] - processing stops after first PDP. Produced result is used as
result of SecHandler.
\item[breakNever] - all PDPs are applied. Result of last PDP is used as result of 
SecHandler.
\end{description}

\subsubsection{Identity Mapping}\label{sec:identitymap-shc}

\subsubsection{Delegation Collector}\label{sec:delegcollector-shc}
\subsubsection{Delegation Handler}\label{sec:deleghandler-shc}
\subsubsection{Username Token}\label{sec:unametoken-shc}
\subsubsection{Username Token}\label{sec:x509token-shc}
%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler

@@

%%% REFERENCES
\end{document}

>>>>

\subsubsection{ARC Authorization}\label{sec:arcauthz-shc}
This Security Handler applies set of Policy Decision Point (PDP) element to the
message and then produces decision result using combining algorithm specified in 
\texttt{action} attribute of \texttt{SecHandler} element. For desciption of PDP
elements see section \ref{sec:Policy Decision Points}. The plugin name of this 
Secirity hadler is \texttt{arc.authz} and it resides in \texttt{arcshc} loadable module.

Available combining algorithms are:
\begin{description}
\item[breakOnDeny] - processing stops when PDP returns Deny decision. The SecHandler
produces negative result. This is a default algorith.
\item[breakOnAllow] - processing stopr when PDP return Allow decision. The SecHandler
produces positive result.
\item[breakAlways] - processing stops after first PDP. Produced result is used as
result of SecHandler.
\item[breakNever] - all PDPs are applied. Result of last PDP is used as result of 
SecHandler.
\end{description}
Here is an example of of ARC Authorization Security Handler configuration.
\begin{lstlisting}[language=xml]
...
  <SecHandler name="arc.authz" event="incoming" id="authz">
    <PDP name="arc.pdp">
      ...
    </PDP>
    <PDP name="xacml.pdp">
      ...
    </PDP>
  </SecHandler>
...
\end{lstlisting}

\subsubsection{Identity Mapping}\label{sec:identitymap-shc}
The Identity Mapping plugin applies set of associated PDPs to the message
being processed and depending on result assigns local account to the 
message. Its plugin name is \texttt{identity.map} and it resides in 
\texttt{identitymap} loading module.

This Security Handler works in a similar way to ARC Authorization (see
section \ref{sec:arcauthz-shc}). But instead of passing results of PDPs as
final processing result it applies local account mapping algorithm 
associated with particular PDP.

Configuration is also similar with only difference being that inside 
each \texttt{PDP} configuration element there is additional element
representing mapping algorithm used for producing local account name.
Available are following mapping algorithms:
\begin{description}
\item[\texttt{LocalName}] - maps to specified account name.
\begin{lstlisting}[language=xml]
...
    <PDP name="arc.pdp">
      <LocalName>nobody</LocalName>
      ...
    </PDP>
...
\end{lstlisting}

\item[\texttt{LocalList}] - uses subject of X.509 certificate presented by client
to perform mapping. Element content provides path to local file containing pairs
of subjects and account names. One pair per line separated by blank space.
\begin{lstlisting}[language=xml]
...
    <PDP name="arc.pdp">
      <LocalList>/etc/grid-security/grid-mapfile</LocalList>
      ...
    </PDP>
...
\end{lstlisting}

\item[\texttt{LocalSimplePool}] - manages dynamic mapping of X.509 client subject
to a set of local accont names. Content of element point to directory containing
file named \texttt{pool}. This file contains list of local account available for
mapping one per line. This directory is also used fro storing currently active
mappings.
\begin{lstlisting}[language=xml]
...
    <PDP name="arc.pdp">
      <LocalSimplePool>/etc/grid-security/mappool</LocalSimplePool>
      ...
    </PDP>
...
\end{lstlisting}
\end{description}

\subsubsection{Delegation Collector}\label{sec:delegcollector-shc}
This plugin processes chain of X.509 certificates and extracts embedded
policies. Policies are attached to the message and may be later used by
Delegation PDP described in section \ref{sec:delegation-pdp}. The
plugin name of this Security Handler is \texttt{delegation.collector} 
and it resides in \texttt{mcctls} loadable module.
It has no configuration parameters.

% \subsubsection{Delegation Handler}\label{sec:deleghandler-shc}

\subsubsection{UsernameToken}\label{sec:unametoken-shc}
The UsernameToken Security Handler processes information in the SOAP Header
stored according to "Web Services Security UsernameToken Profile 1.0"
\cite{ws-security-usernametoken}. The plugin name of this Security Handler
is \texttt{usernametoken.handler} and it resides in \texttt{arcshc} loadable
module.

The configuration element \texttt{Process} defines type of processing to 
be performed. Possible values are:
\begin{description}
\item[extract] - parse and process elements in SOAP Header. This option
shoudl be used for service side configuration.
\item[generate] - create UsernameToken. This option is only used for client
side.
\end{description}

Only another configuration element relevant for service side processing is
\texttt{PasswordSource}. It specifies path to local file containing
list of usernames and passwords (one pair per line) which are accepted 
by plugin. If there is no pair in file matching one SOAP Header this 
Security Handler will raise an error.

\subsubsection{X.509 Token}\label{sec:x509token-shc}
The X.509 Token Security Handler processes information in the SOAP Header
stored according to "Web Services Security X.509 Token Profile 1.0"
\cite{ws-security-usernametoken}. The plugin name of this Security Handler
is \texttt{x509token.handler} and it resides in \texttt{arcshc} loadable
module.

The configuration element \texttt{Process} defines type of processing to 
be performed. Possible values are:
\begin{description}
\item[extract] - parse and process elements in SOAP Header. This option
shoudl be used for service side configuration.
\item[generate] - create X.509 Token. This option is only used for client
side.
\end{description}

In \texttt{extract} mode this plugin process X.509 Token from SOAP Header
and validates contained credetials against locally stored CA certificates.
Following configuration elements specify location of trusted CA certificates:
\begin{description}
\item[CACertificatePath] - path to file containing CA certificate.
\item[CACertificatesDir] - path to directory containing files with CA certificates.
\end{description}
If provided credentials failed verification this Security Handler will raise 
an error.

%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler

@@

\bibliography{grid}
\end{document}
